Evaluating approaches to deriving photometric redshift posterior probability distribution functions for \textsc{LSST}

### 2019-03-09 paper/tex/introduction.tex
typo, adding back some cut content in more appropriate location

Effective astrophysical inference using the catalogs resulting from these ongoing and upcoming missions, however, necessitates accurate and precise photometric redshift (\pz) estimation methodologies.
As an example, in order for \pz\ systematics to not dominate the statistical noise floor of \lsst's main cosmological sample of $\sim 10^{7}$ galaxies, the \lsst\ Science Requirements Document (SRD)\footnote{available at \url{https://docushare.lsstcorp.org/docushare/dsweb/Get/LPM-17}} specifies that individual galaxy \pz s must have root-mean-square error $\sigma_z < 0.02 (1+z)$, $3 \sigma$ ``catastrophic outlier'' rate below $10\%$, and bias below $0.003$.
Specific science cases may have their own requirements on \pz\ performance that exceed those of the survey as a whole.
In that vein, the \lsst\ Dark Energy Science Collaboration (\lsstdesc) developed a separate SRD \citep{Mandelbaum:2018} that conservatively forecasts the constraining power of five cosmological probes, leading to even more stringent requirements on \pz\ performance, including those defined in terms of tomographically binned subsamples populations rather than individual galaxies.

@@

To fully characterize such physical degeneracies, photometric galaxy catalog data releases from \citep{Mandelbaum:2008} to \citep{de_Jong:17}, provided a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the relative probability as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative $\chi^{2}$ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first machine learning based algorithms focused on a point-estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with 1000 realizations scattered within the photometric errors.

@@

This paper is distinguished by its focus on the evaluation criteria for \pzpdf s and interpretation thereof, as part of the mission of the , as a key project of the Photometric Redshift working group of the \lsstdesc\ laid out in the Science Roadmap (SRM)\footnote{Available at: \url{http://lsst-desc.org/sites/default/files/DESC_SRM_V1_1.pdf}}.
In this initial study, we focus on evaluating the performance of \pzpdf\ codes and PDF-specific performance metrics in a controlled experiment with complete and representative prior information (template libraries and training sets).
% Specific implementation choices in each code will influence the resultant posterior distributions, for example choice of prior parameterization in template-based codes, the bandwidth size chosen for machine learning based codes, or even the output format chosen for storing the PDF.
% We have attempted to minimize the impact of many of these factors when comparing codes, for example by using the same template set for all template-based codes, and using a training set that is drawn from the same underlying population as the test sample, to create a controlled environment in which to compare the photo-$z$ PDFs derived from each method.
% We explore a number of performance metrics in this paper that test whether the posterior estimates are actual PDFs.
% Comparing the relative performance of the codes enables us to evaluate whether each code is using information in an optimal way, and may reveal enhancements in some codes and deficiencies in others, either in the fundamental algorithm, or in specific implementation.
% Identifying and fixing failure modes within codes may aid us in reaching the stringent photo-$z$ performance goals set out for LSST.
% We note that these initial tests are a necessary requirement for photo-$z$ codes that will be used in cosmological analyses; however, meeting these requirements is only the first stage in the process, and can be thought of as an initial test under near perfect conditions to test for problems before further complexities are added in future analyses.

>>>>

Effective astrophysical inference using the catalogs resulting from these ongoing and upcoming missions, however, necessitates accurate and precise photometric redshift (\pz) estimation methodologies.
As an example, in order for \pz\ systematics to not dominate the statistical noise floor of \lsst's main cosmological sample of $\sim 10^{7}$ galaxies, the \lsst\ Science Requirements Document (SRD)\footnote{available at \url{https://docushare.lsstcorp.org/docushare/dsweb/Get/LPM-17}} specifies that individual galaxy \pz s must have root-mean-square error $\sigma_z < 0.02 (1+z)$, $3 \sigma$ catastrophic outlier rate below $10\%$, and bias below $0.003$.
Specific science cases may have their own requirements on \pz\ performance that exceed those of the survey as a whole.
In that vein, the \lsst\ Dark Energy Science Collaboration (\lsstdesc) developed a separate SRD \citep{Mandelbaum:2018} that conservatively forecasts the constraining power of five cosmological probes, leading to even more stringent requirements on \pz\ performance, including those defined in terms of tomographically binned subsamples populations rather than individual galaxies.

@@

To fully characterize such physical degeneracies, photometric galaxy catalog data releases from \citep{Mandelbaum:2008} to \citep{de_Jong:17}, provided a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the relative probability as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative $\chi^{2}$ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.

@@

This paper is distinguished by its focus on the evaluation criteria for \pzpdf s and interpretation thereof, as a key project of the Photometric Redshift working group of the \lsstdesc\ that aims to perform a comprehensive sensitivity analysis of \pzpdf\ techniques in order to select those that will become part of the \lsst\ pipelines, as laid out in the Science Roadmap (SRM)\footnote{Available at: \url{http://lsst-desc.org/sites/default/files/DESC_SRM_V1_1.pdf}}.
In this initial study, we focus on evaluating the performance of \pzpdf\ codes using PDF-specific performance metrics in a controlled experiment with complete and representative prior information (template libraries and training sets) to set a baseline for subsequent investigations.
This approach probes how each code considered exploits the information content of the data versus prior information from template libraries and training sets.
